---
title: "02_Greenhouse_Trials"
author: "Matt"
date: "9/14/2020"
output: html_document
---

The intention of this document is to perform scientific analysis of the greenhouse trials performed in my MSc. This will include everything from greenhouse temperature data to biomass and carbon sampling as well.

I'll start with biomass collected in the greenhouse. First, load some packages

```{r}

# library(ggplot2)
# library(ggpubr)
# library(magick)
# library(extrafont)
# library(grid)
# library(multcompView)

library(tidyverse)
library(car)
library(ggpubr)
library(magick)
library(agricolae)
library(extrafont)
if(length(fonts()) == 0) font_import(prompt = FALSE)
loadfonts(device = "win")


```

Next, initialize folders and load the data

```{r}

data_dir <- file.path("./02_Greenhouse/data")
plot_dir <- file.path("./02_Greenhouse/plots")
dir.create(plot_dir, showWarnings = FALSE)
biomass <- read_csv(file.path(data_dir, "greenhouse_raw.csv"), col_types = NULL)
  dplyr::mutate(Soil_Type = factor(Soil_Type, levels = c("Invaded", "Pristine")),
                Soil_Treatment = factor(Soil_Treatment, levels = c("Con", "AC", "Ash")), 
                AboveMass = ifelse(AboveMass == 0.001, 0, AboveMass),
                BelowMass = ifelse(BelowMass == 0.001, 0, BelowMass),
                TotalMass = AboveMass + BelowMass) %>% 
  dplyr::select(Soil_Type, Soil_Treatment, Species, TotalMass)

```

Let's see if the data are normal or not. This requires separating by species since they have very different growth patterns etc.

For both species, test if residuals are significantly different (lots of variation). If so, the data are not normal and something needs to be done to it.

```{r biomass stats}

normal_test <- sapply(unique(biomass$Species), function (x) {
  aov <- aov(TotalMass ~ Soil_Type * Soil_Treatment, 
              data = subset(biomass, Species == x))
  resid <- residuals(aov)
  shapiro <- shapiro.test(resid)$p.value
  levene <- leveneTest(TotalMass ~ Soil_Type * Soil_Treatment,
                        data = subset(biomass, Species == x))$`Pr(>F)`[1]
  return(list(aov = aov, shapiro = shapiro, levene = levene))
}, simplify = FALSE, USE.NAMES = TRUE)

# Neither SK or RF pass the normality test, so I'll transform the data using a 
# log transformation and see if that works. As an aside, only the RF data had
# significantly unequal variances, SK was fine.

biomass$LogMass <- log10(biomass$TotalMass + 1)
normal_test_log <- sapply(unique(biomass$Species), function (x) {
  aov <- aov(LogMass ~ Soil_Type * Soil_Treatment, 
              data = subset(biomass, Species == x))
  resid <- residuals(aov)
  shapiro <- shapiro.test(resid)$p.value
  levene <- leveneTest(LogMass ~ Soil_Type * Soil_Treatment,
                        data = subset(biomass, Species == x))$`Pr(>F)`[1]
  return(list(aov = aov, shapiro = shapiro, levene = levene))
}, simplify = FALSE, USE.NAMES = TRUE)

# The results came back passing all assumptions, and now a proper 2-way ANOVA can
# be carried out:
biomass_anova <- lapply(normal_test_log, function(x) anova(x$aov))

# In both cases, there is a strong 'Soil_Treatment' effect, and a slight interaction
# effect ('Soil_Type:Soil_Treatment'). Use a Tukey test to see where exactly
# the significant differences lie:
tukey <- lapply(normal_test_log, function(x) TukeyHSD(x$aov))

# Most of the differences are from using AC in the soils (which killed everything).

```

After the stats, let's make some figures from that data:

```{r biomass figures}

# First, let's make bar charts for the biomass, and afterwards a boxplot, then 
# finally a side-by-side interaction plot. For the bar chart, we need means and
# standard errors of the LogBiomass data, which means creating a new summarized data table
biomass_summary <- biomass %>% dplyr::group_by(Soil_Type, Soil_Treatment, Species) %>% 
  dplyr::summarise(mean = mean(LogMass), se = sd(LogMass) / sqrt(n()), .groups = "drop")

#This basically tells us that rough fescue performed best in invaded soils. Odd, but it's a result.
#Now, since I mentioned interactions, I should provide interaction plots for visualization purposes
#I will make the plots and then join them with a common legend afterwards
interactions <- sapply(unique(biomass_summary$Species), function(x) {
  p <- ggplot(subset(biomass_summary, Species == x), 
              aes(Soil_Type, mean, group = Soil_Treatment, linetype = Soil_Treatment)) + 
    geom_line(size = 1) +
    geom_point(size = 2) +
    theme_classic(base_size = 14) +
    theme(
      text = element_text(family = "Times New Roman"),
      legend.position = "none",
      legend.background = element_rect(
        fill = "white",
        size = 1,
        linetype = "solid",
        colour = "black"
      ),
      legend.title = element_text(face = "bold"),
      axis.text = element_text(colour = "black"),
      axis.ticks.x = element_blank(),
      axis.ticks.y = element_line(size = 1, linetype = "solid", colour = "black"),
      axis.title = element_text(face = "bold", size = 16),
      axis.title.y = element_text(margin = margin(t = 0, 10, 0, 0)),
      axis.line = element_line(size = 1),
      plot.title = element_text(face = "bold", hjust = 0.5)
    ) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) +
    scale_x_discrete(labels = c("Invaded", "Pristine")) +
    scale_linetype_manual(
      values = c("solid", "dashed", "dotted"),
      name = "Soil Treatment:",
      breaks = c("Con", "AC", "Ash"),
      labels = c("Control", "Activated Carbon", "Ash")
    ) +
    xlab("Soil Type") +
    ylab("Log (Biomass (g) +1)") +
    ggtitle(ifelse(x == "RF", "Rough Fescue", "Spotted Knapweed"))
}, simplify = FALSE, USE.NAMES = TRUE)

#Now join those 2 graphs together
final <- ggarrange(plotlist = interactions, common.legend = TRUE, legend = "bottom") +
  ggsave(filename = file.path(plot_dir, "interactions.png"), width = 6, height = 3, dpi = 300)
#Export image at 600px wide x 300px tall

```

Now onto other old code for updating...

```{r Biomass separated}

rf_img <- image_read(
  "https://live.staticflickr.com/2426/3990317298_1cfbb2e31f_o_d.jpg") %>% 
  image_rotate(90) %>% 
  as.raster()
rf_img_ar <- ncol(rf_img) / nrow(rf_img)

sk_img <- image_read(
  "https://upload.wikimedia.org/wikipedia/commons/2/2d/Centaurea_maculosa_Bozeman.jpg") %>% 
  as.raster()
sk_img_ar <- ncol(rf_img) / nrow(rf_img)

biomass_plot <- sapply(unique(biomass_summary$Species), function(x) {
  df <- subset(biomass, Species == x) %>% 
    unite(trt, c("Soil_Type", "Soil_Treatment"), remove = FALSE) %>% 
    dplyr::mutate(Soil_Treatment = factor(Soil_Treatment, levels = c("AC", "Ash", "Con")))
  df_summary <- subset(biomass_summary, Species == x) %>% 
    unite(trt, c("Soil_Type", "Soil_Treatment"), remove = FALSE) %>% 
    dplyr::mutate(Soil_Treatment = factor(Soil_Treatment, levels = c("AC", "Ash", "Con")))
  
  # Get significance letters using HSD.test from agricolae package
  df_summary <- HSD.test(aov(LogMass ~ trt, data = df),trt = "trt", group = TRUE)$groups %>% 
    rownames_to_column("trt") %>% 
    dplyr::select(-LogMass) %>% 
    merge(df_summary)
  
  p <- ggplot(subset(df_summary, Species == x), 
              aes(Soil_Treatment, mean, fill = Soil_Type)) +
    geom_bar(
      stat = "identity",
      position = "dodge",
      colour = "black",
      size = 1) +
    geom_errorbar(
      aes(ymin = mean - se, ymax = mean + se),
      size = 1,
      width = 0.3,
      position = position_dodge(0.9)) +
    ggtitle(ifelse(x == "RF", "Rough Fescue", "Spotted Knapweed")) +
    xlab("Soil Amendment") +
    ylab("Log (Biomass (g) + 1)") +
    scale_fill_manual(
      values = c("#5a5a5a", "#adadad"),
      breaks = c("Invaded", "Pristine"),
      labels = c("Invaded", "Pristine"),
      name = "Soil Type:") +
    theme_classic(base_size = 14) +
    theme(
      rect = element_rect(fill = "transparent"),
      text = element_text(family = "Times New Roman"),
      legend.position = c(0.12, 0.88),
      legend.background = element_rect(
        fill = "white",
        size = 1,
        linetype = "solid",
        colour = "black"),
      legend.title = element_text(face = "bold", size = 16),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      axis.text = element_text(colour = "black"),
      axis.ticks.x = element_blank(),
      axis.ticks.y = element_line(size = 1, linetype = "solid", colour = "black"),
      axis.title = element_text(face = "bold", size = 16),
      axis.title.y = element_text(margin = margin(t = 0, 10, 0, 0)),
      axis.line = element_line(size = 1),
      plot.title = element_text(face = "bold", hjust = 0.5)) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 1)) +
    scale_x_discrete(labels = c(AC = "AC", Ash = "Ash", Con = "Control")) +
    geom_text(
      aes(label = groups, y = mean + se),
      position = position_dodge(0.9),
      vjust = -0.5,
      family = "serif", 
      size = 5)
}, simplify = FALSE, USE.NAMES = TRUE)

biomass_plot <- ggarrange(plotlist = biomass_plot, common.legend = TRUE, legend = "bottom") +
  ggsave(file.path(plot_dir, "bmass.png"), width = 6, height = 3, dpi = 300)

# If images are to be included, run the following lines:
final <- biomass_plot + 
  annotation_raster(rf_img, xmin = 0.14, 
                    xmax = 0.24,
                    ymin = 0.6,
                    ymax = 0.85) + 
  annotation_raster(sk_img, xmin = 0.64, 
                    xmax = 0.74,
                    ymin = 0.6,
                    ymax = 0.85) + 
  ggsave(file.path(plot_dir, "bmass_with_images.png"), width = 6, height = 3, dpi = 300)

```

I need to do some stuff with survival of the planted greenhouse plants as well:

```{r}

surv <- read_csv(file.path(data_dir, "greenhouse_raw.csv"), col_types = NULL) %>% 
  dplyr::select(-c(AboveMass, BelowMass, Rep)) %>% 
  dplyr::mutate(Soil_Type = factor(Soil_Type, levels = c("Invaded", "Pristine")),
                Soil_Treatment = factor(Soil_Treatment, levels = c("Con", "AC", "Ash")), 
                germ_rat = Germinants / 5, 
                deaths = Germinants - Survival, 
                trial_surv = Survival / 5, 
                germ_surv = ifelse(Survival == 0 & Germinants == 0, 0, 
                                   Survival / Germinants))

surv_summary <- group_by(surv, Soil_Type, Soil_Treatment, Species) %>% 
  summarise(across(c(germ_rat, deaths, trial_surv, germ_surv), 
                   list(mean = mean, se = ~sd(.x) / sqrt(n()))), .groups = "drop")

plots <- names(surv_summary)[endsWith(names(surv_summary), "mean")]

aovs <- sapply(plots, function(x) {
  df <- dplyr::rename(surv, data = all_of(gsub("_mean", "", x)))
  iter <- sapply(unique(df$Species), function(x) {
    aov <- aov(data ~ Soil_Type * Soil_Treatment, 
               data = subset(df, Species == x))
    resid <- residuals(aov)
    shapiro <- shapiro.test(resid)$p.value
    levene <- leveneTest(data ~ Soil_Type * Soil_Treatment,
                         data = subset(df, Species == x))$`Pr(>F)`[1]
    return(list(aov = aov, shapiro = shapiro, levene = levene))
  }, simplify = FALSE, USE.NAMES = TRUE)
}, simplify = FALSE, USE.NAMES = TRUE)

surv_log <- mutate(surv, across(starts_with(gsub("_mean", "", plots)), ~log10(.x + 1)))
surv_log_summary <- group_by(surv_log, Soil_Type, Soil_Treatment, Species) %>% 
  summarise(across(c(germ_rat, deaths, trial_surv, germ_surv), 
                   list(mean = mean, se = ~sd(.x) / sqrt(n()))), .groups = "drop")

aovs_log <- sapply(plots, function(x) {
  df <- dplyr::rename(surv_log, data = all_of(gsub("_mean", "", x)))
  iter <- sapply(unique(df$Species), function(x) {
    aov <- aov(data ~ Soil_Type * Soil_Treatment, 
               data = subset(df, Species == x))
    resid <- residuals(aov)
    shapiro <- shapiro.test(resid)$p.value
    levene <- leveneTest(data ~ Soil_Type * Soil_Treatment,
                         data = subset(df, Species == x))$`Pr(>F)`[1]
    return(list(aov = aov, shapiro = shapiro, levene = levene))
  }, simplify = FALSE, USE.NAMES = TRUE)
}, simplify = FALSE, USE.NAMES = TRUE)

surv_plots <- sapply(plots, function(x) {
  
  df <- dplyr::select(surv, Soil_Type, Soil_Treatment, Species, all_of(gsub("_mean", "", x))) %>% 
    dplyr::mutate(Soil_Treatment = factor(Soil_Treatment, levels = c("AC", "Ash", "Con"))) %>% 
    unite(trt, c("Soil_Type", "Soil_Treatment"), remove = FALSE) %>% 
    dplyr::rename(data = all_of(gsub("_mean", "", x)))
  
  df_summary <- dplyr::select(
    surv_summary, 
    Soil_Type, Soil_Treatment, Species, all_of(c(x, gsub("_mean", "_se", x)))) %>% 
    dplyr::mutate(Soil_Treatment = factor(Soil_Treatment, levels = c("AC", "Ash", "Con"))) %>% 
    unite(trt, c("Soil_Type", "Soil_Treatment"), remove = FALSE) %>% 
    dplyr::rename(mean = all_of(x), 
                  se = all_of(gsub("_mean", "_se", x)))
  
  iter <- sapply(unique(df$Species), function(y) {
    df2 <- dplyr::filter(df, Species == y)
    df_summary2 <- dplyr::filter(df_summary, Species == y)
    
    df_summary2 <- HSD.test(aov(data ~ trt, data = df2), trt = "trt", group = TRUE)$groups %>% 
      rownames_to_column("trt") %>% 
      dplyr::select(-data) %>% 
      merge(df_summary2)
    
    p <- ggplot(df_summary2, aes(Soil_Type, mean, fill = Soil_Treatment)) + 
      geom_bar(stat = "identity", position = "dodge", colour = "black", size = 1) +
      geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                    size = 1, width = 0.3, position = position_dodge(0.9)) +
      ggtitle(ifelse(x == plots[1], ifelse(y == "RF", "Rough Fescue", "Spotted Knapweed"), "")) +
      xlab("Soil Site")+
      ylab(paste0(ifelse(
        x == "germ_rat_mean", "Germination Rate\nafter 1 month", ifelse(
          x == "deaths_mean", "Mean deaths\nper pot", ifelse(
            x == "trial_surv_mean", "90-day Survival Rate", 
            "Survival Rate of\nGerminated Individuals"))))) +
      theme_classic(base_size = 16) +
      theme(
        text = element_text(family = "Times New Roman"),
        legend.position = c(0.18, 0.88),
        legend.background = element_rect(
          fill = "white", size = 1,linetype = "solid", colour = "black"),
        legend.title = element_text(face = "bold", size = 18),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_text(colour = "black"),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_line(size = 1, linetype = "solid", colour = "black"),
        axis.title = element_text(face = "bold", size = 16),
        axis.title.y = element_text(margin = margin(t = 0, 10, 0, 0)),
        axis.line = element_line(size = 1), 
        plot.title = element_text(face = "bold", hjust = 0.5)) +
      scale_fill_manual(
        values = c("dimgray", "darkgray", "gainsboro"),
        breaks = c("AC","Ash","Con"),
        labels = c("Activated Carbon", "Ash", "Control"),
        name = "Soil Amendment:") +
      scale_y_continuous(
        expand = c(0, 0), 
        limits = c(0, ifelse(x == "deaths_mean", 5, 1.25))) +
      scale_x_discrete(labels = c(Invaded = "Invaded", Pristine = "Pristine")) +
      geom_text(aes(label = groups, y = mean + se), position = position_dodge(0.9),
                vjust= -0.5, family = "serif", size = 5)
    
  }, simplify = FALSE, USE.NAMES = TRUE)
  
  # final <- ggarrange(plotlist = iter, common.legend = TRUE, legend = "none")
  
}, simplify = TRUE, USE.NAMES = TRUE)

final <- ggarrange(plotlist = surv_plots, common.legend = TRUE, legend = "bottom", 
                   ncol = 2, nrow = 4) +
  ggsave(filename = file.path(plot_dir, "survival.png"), width = 8.5, height = 11, dpi = 300)
  

```



Shifting gears to the elemental analyzer data now:

```{r}

analyzer <- read.csv(file.path(data_dir, "Analyzer.csv"))

elements <- names(dplyr::select(analyzer, where(is.numeric)))
el_aov <- sapply(elements, function(x) {
  form <- as.formula(paste0(x, "~ Soil_Type * Soil_Treatment"))
  aov(form, data = analyzer)
}, simplify = FALSE, USE.NAMES = TRUE)

el_residuals <- lapply(el_aov, residuals)
el_shapiro <- lapply(el_residuals, shapiro.test)
el_levine <- sapply(elements, function(x) {
  form <- as.formula(paste0(x, "~ Soil_Type * Soil_Treatment"))
  leveneTest(form, data = analyzer)
}, simplify = FALSE, USE.NAMES = TRUE)
el_anova <- lapply(el_aov, anova)
el_tukey <- lapply(el_aov, TukeyHSD)

analyzer_summary <- group_by(analyzer, Soil_Type, Soil_Treatment) %>% 
  dplyr::summarise(across(where(is.numeric), list(mean = mean, se = ~sd(.x) / sqrt(n()))), .groups = "drop")

analyzer_plots <- sapply(elements, function(x) {
  df <- dplyr::select(analyzer, c(Soil_Type, Soil_Treatment, all_of(x))) %>% 
    unite(trt, c("Soil_Type", "Soil_Treatment"), remove = FALSE) %>% 
    dplyr::mutate(Soil_Treatment = factor(Soil_Treatment, levels = c("AC", "Ash", "Con"))) %>% 
    dplyr::rename(data = 4)
  
  df_summary <- dplyr::select(analyzer_summary, c(Soil_Type, Soil_Treatment, starts_with(x))) %>% 
    dplyr::rename(mean = 3, se = 4) %>% 
    dplyr::mutate(Soil_Treatment = factor(Soil_Treatment, levels = c("AC", "Ash", "Con"))) %>% 
    unite(trt, c("Soil_Type", "Soil_Treatment"), remove = FALSE)
  
  # Get significance letters using HSD.test from agricolae package
  df_summary <- HSD.test(aov(data ~ trt, data = df), trt = "trt", group = TRUE)$groups %>% 
    rownames_to_column("trt") %>% 
    dplyr::select(-data) %>% 
    merge(df_summary)
  
  # Used to produce bar plots but not useful, boxplot more interpretable
  # p <- ggplot(df_summary, aes(Soil_Type, mean, fill = Soil_Treatment)) + 
  #   geom_bar(stat = "identity", position = "dodge", colour = "black", size = 1) +
  #   geom_errorbar(aes(ymin = mean - se, ymax = mean + se), 
  #                 size = 1, width = 0.3, position = position_dodge(0.9)) +
  #   xlab("Soil Site")+
  #   ylab(paste0("Total ", x, " (%)")) +
  #   theme_classic(base_size = 16) +
  #   theme(
  #     text = element_text(family = "Times New Roman"),
  #     legend.position = c(0.18, 0.88), 
  #     legend.background = element_rect(
  #       fill = "white", size = 1,linetype = "solid", colour = "black"),
  #     legend.title = element_text(face = "bold", size = 18),
  #     panel.grid.major = element_blank(),
  #     panel.grid.minor = element_blank(),
  #     axis.text = element_text(colour = "black"),
  #     axis.ticks.x = element_blank(),
  #     axis.title = element_text(face = "bold", size = 18)) + 
  #   scale_fill_manual(
  #     values = c("dimgray", "darkgray", "gainsboro"),
  #     breaks = c("AC","Ash","Con"),
  #     labels = c("Activated Carbon", "Ash", "Control"),
  #     name = "Soil Amendment") +
  #   scale_y_continuous(
  #     expand = c(0, 0), 
  #     limits = c(0, max(ceiling(df_summary$mean)))) +
  #   scale_x_discrete(labels = c(Invaded = "Invaded", Pristine = "Pristine")) +
  #   geom_text(aes(label = groups, y = mean + se), position = position_dodge(0.9), 
  #             vjust= -0.5, family = "serif", size = 5)
  
  p <- ggplot(df, aes(Soil_Type, data, fill = Soil_Treatment)) +
    geom_boxplot(lwd = 0.6, color = "black", width = 1) +
    xlab("Soil Site") +
    ylab(paste0("Total ", x, " (%)"))  +
    theme_classic(base_size = 14) +
    theme(
      text = element_text(family="Times New Roman"), 
      legend.position = c(0.18, 0.88),
      legend.background = element_rect(
        fill = "white", size = 1, linetype = "solid", colour = "black"),
      legend.title = element_text(face = "bold",size = 16), 
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      axis.text = element_text(colour = "black"),
      axis.ticks.x = element_blank(),
      axis.ticks.y = element_line(size = 1, linetype = "solid", colour = "black"),
      axis.title = element_text(face = "bold",size = 16),
      axis.title.y = element_text(margin = margin(t = 0, 10, 0, 0)),
      axis.line = element_line(size = 1)) +
    scale_fill_manual(
      values = c("gray99", "gray66", "gray33"),
      breaks = c("AC", "Ash", "Con"),
      labels = c("Control", "Activated Carbon", "Ash"), 
      name = "Soil Amendment:") +
    scale_x_discrete(labels = c(INV = "Invaded", PRI = "Pristine")) +
    scale_y_continuous(
      expand = c(0, 0), 
      limits = c(
        ifelse(max(df$data) < 1 | max(df$data) - min(df$data) < 1, 
               round(min(df$data) - 0.1, digits = 1), min(floor(df$data))),
        ifelse(max(df$data) < 1 | max(df$data) - min(df$data) < 1, 
               round(max(df$data) + 0.1, digits = 1), max(ceiling(df$data)))))
}, simplify = FALSE, USE.NAMES = TRUE)

# Arrange final plot of carbon and nitrogen only
final <- ggarrange(plotlist = analyzer_plots[2:1], common.legend = TRUE, legend = "bottom") +
  ggsave(filename = file.path(plot_dir, "CN_plot.png"), width = 6, height = 3, dpi = 300)

```

